Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-22 doc/LinksToDAG_final.tex
resolved some TODOs

We worried that the direction mapping might be unstable and sensitive to the input corpus.  Happily, Figure~\ref{fig:convergence} shows otherwise (for both English and Russian). \noteJE{IMPORTANT! current graph is with fine-grained tags; rerun with the coarse-grained tags as in the rest of the paper} Using even a small prefix of the data got very high-precision results, in the sense that nearly all $r_L$ or $\ell_L$ variables that were 1 in this lightly trained mapping were also 1 in our largest run.  The only disadvantage to using small data is low recall relative to the large run---many of the labels $L$ are not observed yet and so we do not yet allow either direction ($r_L=\ell_L=0$).

@@

Recall that \url{http://www.abisource.com/projects/link-grammar/dict/summarize-links.html} documents the 122 link types in the English link grammar lexicon.  Below is the result of our largest English run, whose corpus uses \input{figure/allowed_labels_total.tex}of these types. \noteJH{automatically generate this number correctly: 107}

>>>>

We worried that the direction mapping might be unstable and sensitive to the input corpus.  Happily, Figure~\ref{fig:convergence} shows otherwise (for both English and Russian). \noteJE{IMPORTANT! current graph is with fine-grained tags; rerun with the coarse-grained tags as in the rest of the paper} \noteJH{done} Using even a small prefix of the data got very high-precision results, in the sense that nearly all $r_L$ or $\ell_L$ variables that were 1 in this lightly trained mapping were also 1 in our largest run.  The only disadvantage to using small data is low recall relative to the large run---many of the labels $L$ are not observed yet and so we do not yet allow either direction ($r_L=\ell_L=0$).

@@

Recall that \url{http://www.abisource.com/projects/link-grammar/dict/summarize-links.html} documents the 122 link types in the English link grammar lexicon.  Below is the result of our largest English run, whose corpus uses \input{figure/allowed_labels_total.tex}of these types.
